\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects and Parallel-Jaw Grasps and a Multi-Armed Bandit Algorithm with Correlated Rewards for Robust Grasp Planning at Scale \versionline{4}

### 2015-09-10 ICRA2016/bandits_docs/includes/dataset.tex
Modified entire draft. In a limbo state. Going back through feedback now.

\section{Dexterity Network}
\seclabel{dexnet}
\TODO{Due to space, it might make sense to discuss in experiments as appears to be common practice when the dataset is not going to be released to the public}
It remains to describe the details of creating the Dexterity Network (Dex-Net), our prior dataset of objects and grasps with similarity, for use in the Multi-Armed Bandit models of Algorithm~\ref{alg:full}.
Dex-Net 1.0 consists of approximately 20,162 3D mesh models \TODO{Update with correct count} collected from the datasets described in \figref{datasets}.
Laser-scanned models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking} constitute 355 of the total models.
These models were chosen to reflect physical objects commonly used for benchmarking in grasping research for potential future physical experiments using Dex-Net.
The majority of Dex-Net is synthetic 3D mesh models from 3DNet\cite{wohlkinger20123dnet}, a benchmark for object detection in robotics research,  ModelNet~\cite{wu20143d}, a relatively new benchmark for 3D model classification, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison}, a competition benchmark with many categories to test the state-of-the-art in shape retrieval annually.
While the geometry of synthetic models does not necessarily reflect a physical object, using these models allows us to examine the effects of scale at tens of thousands of 3D models, which has not been previously attempted in grasp synthesis research.

In order to use the models for grasp selection, we first preprocess each model.
Each object in Dex-Net is originally specified as a 3D mesh $\mS = \{\mV, \mT\}$ where $\mV = \{\bv_1, ..., \bv_V\}$ is a set of $V$ vertices such that $\bv_i \in \bR^3$ for $i = 1, ..., V$ and $\mT = \{t_1, ..., t_F\}$  is a set of $F$ triangles such that $t_j \in \mathbb{Z}_{+}^3$ for $j = 1, ..., F$.
First, we remove unreferenced vertices and illegal triangles (e.g. same vertex is referenced twice in one triangle).
Next, we normalize the orientation of the model by performing Principal Component Analysis (PCA) on the raw vertices of the mesh and then rotating the object such that its first principal component aligns with the $z$-axis and its second aligns with the $y$-axis.
We then set the object center of mass $\bz$ to be the center of the bounding box for the reoriented mesh.
Since synthetic models may not be specified in meters, we also rescale each mesh such that the smallest dimension of the bounding box lies withing the maximum opening of the gripper.
Finally, we convert each mesh to a signed distance field $f$ using SDFGen~\cite{}, an open-source C++ tool.

Once each 3D model is preprocessed, we compute the shape feature vector described in \secref{cnn} for each object.
Each feature vector is then put into a KD-Tree nearest neighbor query structure for accelerated lookups of shape nearest neighbors.
This structure consistutes our shape similiarity network, in which each object $\mO$  is connected to its $n$ nearest neighbors $\mO_1, ..., \mO_n$ by an edge of weight $\| \psi(\mO) - \psi(\mO_i) \|_2^2$.
We generate a set of grasps for each object in the network using the method of \secref{candidates} and evaluate the probability of force closure for each grasp using brute-force Monte Carlo integration as a benchmark~\cite{kehoe2012toward}.
As the number of models is quite large, we distribute the grasp labelling for each object across virtual machines in Google Compute Engine and aggregate the results at the end.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.1]{figures/dataset_table.jpg}
\caption{The seven datasets used in Dex-Net 1.0 with information on whether or not the models were laser-scanned, the number of models in the dataset, and the number of labelled categories (if category labels are present). \TODO{Update ModelNet number - we actually only use select categories}}
\figlabel{datasets}
\vspace*{-15pt}
\end{figure}

>>>>

\section{Dexterity Network}
\seclabel{dexnet}

\TODO{Make this flow with above paragraph!}
The Dexterity Network (Dex-Net) 1.0, is a dataset of prior 3D object models annotated with parallel-jaw grasps and a similarity metric to efficiently index objects.
Dex-Net consists of over 10,000 3D mesh models, selected to represent objects that might be encountered in warehousing or the home such as tableware, tools, and toys.
%Laser-scanned models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking} constitute 355 of the total models.
%The majority of Dex-Net is synthetic 3D mesh models from 3DNet\cite{wohlkinger20123dnet}, a benchmark for object detection in robotics research,  ModelNet~\cite{wu20143d}, a benchmark for 3D model classification, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison}, a competition benchmark with many categories to test the state-of-the-art in shape retrieval annually.
\figref{datasets} details the data sources and their sizes.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.1]{figures/dataset_table.jpg}
\caption{The seven datasets used in Dex-Net 1.0 with information on whether or not the models were laser-scanned, the number of models in the dataset, and the number of labelled categories (if category labels are present).}
\figlabel{datasets}
\vspace*{-15pt}
\end{figure}

\subsection{Data Cleaning}
Each object in Dex-Net is originally specified as a 3D mesh $\mX = \{\mV, \mT\}$ where $\mV = \{\bv_1, ..., \bv_V\}$ is a set of $V$ vertices such that $\bv_i \in \bR^3$ for $i = 1, ..., V$ and $\mT = \{t_1, ..., t_F\}$  is a set of $F$ triangles such that $t_j \in \mathbb{Z}_{+}^3$ for $j = 1, ..., F$.
We preprocess each model by first removing unreferenced vertices and degenerate triangles.
Next, we compute the object reference frame by performing Principal Component Analysis (PCA) on the vertices of the mesh and aligning the $z$-axis with the first principal component and the $y$-axis with the second principal component
We then set the object center of mass $\bz$ to be the center of the bounding box for the reoriented mesh.
Since synthetic models may not be specified in meters, we also rescale each mesh such that the smallest dimension of the bounding box lies within $w = 0.1m$, which is approximately the maximal opening width of a PR2 gripper.
Finally, we convert each mesh to a signed distance field $f$ using SDFGen~\cite{sdfgen}, an open-source C++ tool.

\subsection{Grasp Sampling}
\seclabel{grasp-sampling}
Each 3D object $\mO_i$ in Dex-Net is labelled with up to 250 parallel-jaw grasps and the $P_F$ for each.
We generate candidate grasps using a modified version of the 2D algorithm presented in Smith et al.~\cite{smith1999computing} to concentrate samples on grasps that are antipodal~\cite{mahler2015gp}.
Let $w$ be the maximal opening of the gripper, $\hat{\gamma}$ be a sampled friction coefficient, and $\mS $ be the set of points on the object surface for an SDF $f$ as described in \secref{grasp-param}.
To sample a single grasp, we first generate a contact point $\bc_1$ by sampling uniformly from $\mC$ using rejection sampling.
Next we sample a direction $\bv \in \bS^2$ uniformly at random from the cone and compute:
%\vspace{-2ex}
\begin{align*}
	\bc_2 = \bc_1 + (w / 2 - t_2^*) \bv  &&  \bx = 0.5 (\bc_1 + \bc_2)
\end{align*}
\noindent where $t_2^*$ is defined in \secref{contact}.
This yields a grasp $\bg_{i,k} = (\bx, \bv)$.
We add $\bg_{i,k}$ to our candidate set if both $\bv^T \bn_1 \leq \cos(\arctan(\hat{\gamma}))$ and $\bv^T \bn_2 \leq \cos(\arctan(\hat{\gamma}))$.

We then evaluate $P_F(\bg)$ using Monte-Carlo integration~\cite{kehoe2012toward} by sampling the object pose, gripper pose, and friction random variables $N_s$ times and recording $S_{i,k}$, the number of samples for which grasp $\bg_{i,k}$ was in force closure.
Formally, our full dataset of $N_o$ 3D objects and $N_g$ grasps per object is $\mD = \{ (S_{i, k}, \mY_{i, k}) \big| i = \{1, ..., N_o\}, k = \{1, ..., N_g\} \}$ where $\mY_{i,k} = (\bg_{i, k}, \mO_i) \in \mM$ is a grasp-object pair in our Grasp Moduli Space.

%We generate a set of grasps for each object in the network using the method of \secref{candidates} and evaluate the probability of force closure for each grasp using brute-force Monte Carlo integration as a benchmark~\cite{kehoe2012toward}.
%As the number of models is quite large, we distribute the grasp labelling for each object across virtual machines in Google Compute Engine and aggregate the results at the end.

\subsection{Object Similarity Embedding}
\seclabel{object-similarity}
In order to efficiently index prior 3D object and grasp data from Dex-Net, we embed each object in a Euclidean feature space in which similar objects are close together.
Our similarity embedding is based on multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape retrieval that uses the powerful features leared by CNNs on millions of images~\cite{krizhevsky2012imagenet}.

\figref{global-feature-model} illustrates our method.
Let $R$ be the maximum dimension of the object bounding box.
We first render every object on a white background in a total of $N_c = 50$ virtual camera views oriented toward the object center and discretized on a viewing sphere along angle increments $\delta_{\theta} = \frac{4 \pi}{N_c}$ and $\delta_{\phi} = \frac{2 \pi}{N_c}$ and radii $r = R, 2R$.
Then we train a CNN with the architecture of AlexNet~\cite{krizhevsky2012imagenet} to predict the 3D object class label for the rendered images on a training set of models. 
We initialize the weights of our network with the weights learned on ImageNet by Krizhevsky et al.~\cite{krizhevsky2012imagenet} and optimize using Stochastic Gradient Descent (SGD). 
Next, we pass each of the $N_c$ views of each object through the optimized CNN and max-pool the output of the fc7 layer, the highest layer of the network before the class label prediction. 
Finally, we use Principal Component Analysis (PCA) to reduce the max-pooled output to from 4028 dimensions to 100 dimensions.
This yields our representation $\psi(\mO) \in \mathbb{R}^{100}$ for each object.
Our method differs from the MV-CNN of Su et al.~\cite{su2015multi} because we use PCA for the final output, while Su et al. use a second CNN on the output of the pooled views.

Given the MV-CNN object representation, we measure the dissimilarity between two objects $\mO_i$ and $\mO_j$ by the Euclidean distance $\| \psi(\mO_i) - \psi(\mO_j) \|_2$.
For efficient lookups of similar objects, Dex-Net contains a KD-Tree nearest neighbor query structure with the feature vectors of all prior objects.

%In our implementation, we trained our MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models from the SHREC 2014 dataset ~\cite{li2015comparison} for 500,000 iterations of SGD, and the final PCA step captured approximately 85\% of the variance of the vectors.
%The image classification training step had a test accuracy of 76\%.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.3]{figures/illustrations/cnn_model.png}
\caption{Illustration of our method for embedding 3D object models in a Euclidean vector space for computing global shape similiarty. We pass a set of 50 virtually rendered camera viewpoints discretized around a sphere through a deep Convolutional Neural Network (CNN) with the AlexNet~\cite{krizhevsky2012imagenet} architecture. Finally, we take the maximum fc7 response across each of the 50 views for each dimension and run PCA to reduce the dimensionality of the output.}
\figlabel{global-feature-model}
\vspace*{-15pt}
\end{figure}

### 2015-09-10 ICRA2016/bandits_docs/includes/experiments.tex
Modified entire draft. In a limbo state. Going back through feedback now.

\TODO{All experiments here are preliminary. Add new results from non-symmetric objects and more data}
\TODO{Include experiments on sensitivity to uncertainty} \\
\TODO{Images of selected grasps} \\

We evaluated the convergence rate of Algorithm~\ref{alg:full} for varying sizes of prior data used from Dex-Net and examined the sensitivity to parameters of the algorithm.
To test the generalization of our feature maps, we reserved objects from YCB and ModelNet as a test set, and used nested subsets of the remaining data as training data for optimizing the hyperparameters and for tuning the MAB convergence rate.
We assumed a PR2 gripper for our grasps, which has a maximum width of approximately $10cm$.
We assumed isotropic covariance with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.
The weights of our similarity kernel were selected using a grid search over possible values on a held-out validation set.

\subsection{System}
To handle the scale of the experiments, we developed a Cloud-based software library on top of Google Cloud services.
We used Google Cloud Storage (GCS) to store the mesh models and to sample and evaluate 250 grasps per object.
We used Google Compute Engine to distribute trials of MAB algorithms across objects, reducing the runtime of our large-scale experiments.
Our master analysis script can launch up to 600 GCE single core instances, each running Ubuntu 12.04.
When an instance is launched, we mounted Dex-Net via a persistent disk containing a particular set of objects and grasps.
Each instance pulls our latest code from Github, runs a single python experiment script configured in a YAML file, compresses the results in an output directory, and uploads the results to GCS.
After all instances complete, the master script turns off all instances, unmounts all disks, downloads the results from each instance, and sends the user a notification email.
The results can be optionally analyzed by the master script.

@@

~\figref{local-mab} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the $P_F$ in the candidate grasp set) versus iteration averaged over 20 trials for a cereal box and flower pot.
The plot compares Algorithm~\ref{alg:full} with no prior data to uncorrelated Thompson sampling and uniform allocation, two methods used by Laskey et al.~\cite{laskey2015bandits}.
We see that the CCBP model outperforms the uncorrelated model by approximately 10$\times$ for the cereal box but has comparable performance to Thompson sampling on the flower pot.
Iniitial reuslts suggest that performance on the flower pot is poorer because few grasps are similar according to our feature representation.

>>>>

\TODO{All experiments here are preliminary. Add new results from more objects, especially non-symmetric ones.} \\
\TODO{Include experiments on sensitivity to uncertainty.} \\
\TODO{Images of selected grasps.} \\

We evaluated the convergence rate of Algorithm~\ref{alg:full} for varying sizes of prior data used from Dex-Net and examined the sensitivity of the convergence rate to the kernel bandwidths, number of nearest neighbors, and uncertainty.
We created three nested training sets of 100, 1000, and 10000 objects by uniformly sampling objects from Dex-Net.
From the remaining objects we created a set of 20 validation objects for selecting algorithm hyperparameters and a set of 30 objects for test data.
We used isotropic covariance with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.
The bandwidths of our similarity kernel were set to scaling transformations $C = \sigma I$ where $\sigma \in \bR$ for the grasp parameter and global object feature maps, and a gaussian mask $C_d$ centered on the gradient heightmaps with height $w_d \in \bR$ and variance $\sigma_d \in \bR$.
The bandwidths were selected by maximizing convergence rate on the validation set using a grid search over hyperparameters.

To handle the scale of the experiments, we developed a Cloud-based software library on top of Google Cloud Platform.
We used Google Compute Engine to distribute trials of MAB algorithms across objects and Google Cloud Storage (GCS) to store Dex-Net.
Our experimental scripts launched up to 1500 GCE single core instances at one time for hyperparameter tuning and convergence analysis, reducing the runtime of our experiments by a factor of nearly $1500\times$.

@@

~\figref{local-mab} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ in the candidate grasp set) versus iteration averaged over 20 trials for a cereal box and flower pot.
The plot compares Algorithm~\ref{alg:full} with no prior data to uncorrelated Thompson sampling and uniform allocation, two methods used by Laskey et al.~\cite{laskey2015bandits}.
We see that the CCBP model outperforms the uncorrelated model by approximately 10$\times$ for the cereal box but has comparable performance to Thompson sampling on the flower pot.
Iniitial reuslts suggest that performance on the flower pot is poorer because few grasps are similar according to our feature representation.

### 2015-09-10 ICRA2016/bandits_docs/includes/introduction.tex
Modified entire draft. In a limbo state. Going back through feedback now.

Consider a robot fulfilling orders in a warehouse.
The robot must quickly plan grasps for consumer products to fullfill orders.
Furthermore, the robot may not precisely know the state of the environment, such as the pose or frictional properties of object, due to sensor imprecision and missing data (e.g. occlusions in point clouds).
This poses a challenge for many existing grasp planning methods that are based on precise knowledge of contact locations and surface normals~\cite{ciocarlie2009, ferrari1992} due to the distribution on possible environment configurations.

In vision and speech, advances in Big Data and distributed computing, combined with datasets of milliions of examples such as ImageNet~\cite{deng2009imagenet} and the Fisher corpus~\cite{cieri2004fisher}, have produced impressive results~\cite{hannun2014deepspeech, hays2008im2gps, krizhevsky2012imagenet} that surpass those obtained from decades of research on analytic methods.
This raises the question: will machine learning of grasps for vast numbers of possible object poses, object shapes, environment configurations, etc., exhibit scaling effects similar to those observed in computer vision and speech recognition?

@@

We introduce Dex-Net 1.0, a dataset of 3D models and grasps with similarity metrics, and a system for actively acquiring statistical models of grasp quality across the network.
The Dex-Net dataset contains representative 3D models of objects that could be encountered in warehousing or the home.
Dex-Net contains laser-scanned 3D mesh models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking} to reflect physical objects commonly used for benchmarking in grasping research.
The dataset also includes synthetic 3D mesh models from shape classification datasets such as 3DNet~\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20143d}, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison} to scale the number of models.
~\figref{dexnet-teaser} shows a sample of the objects in the dataset.
We measure object similarity based the distance between feature vectors generated from multi-view Convolutional Neural Networks (CNNs)~\cite{su2015multi}, a state-of-the are method in shape retrieval
We measure similarity between grasps by the pose of the gripper and local surface ``heightmaps" extracted at location of contact with an object~\cite{herzog2012template, kappler2015leveraging}.
Our system uses Google Cloud Platform to distribute grasp quality evaluations across hundreds of virtual machines and to store millions of grasps across the objects in Dex-Net.

In this work, we use Dex-Net to study the convergence rate of Multi-Armed Bandit (MAB) algorithms for finding a grasp with high probability of force closure under object pose, gripper pose, and friction coefficient uncertainty from a set of 250 candidate grasps on objects from Dex-Net.
To do so, we extend the MAB framework of Laskey et al.~\cite{laskey2015bandits} to model correlations between the probability of force closure for similar grasps on similar 3D objects using Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}.
CCBPs predict a belief distribution for the quality of each grasp based similarity to data in Dex-Net that can be efficiently updated after observing the quality of a grasp for a sampled object pose, gripper pose, and friction coefficient.
Our results suggest that CCBPs bootstrapped with data from Dex-Net can accelerate grasp planning by up to $10\times$.

>>>>

``Cloud Robotics and Automation" considers a new paradigm where robots and automation systems exchange data and perform computation via networks instead of operating in isolation with limited computation and memory.
There are several potential advantages to using the Cloud: 1) Big Data: access to updated libraries of images, maps, and object/product data, 2) Cloud Computing: access to parallel grid computing for statistical analysis, machine learning, and planning.
These advantages have recently been highlighted in vision and speech, where datasets with millions of examples such as ImageNet~\cite{deng2009imagenet} and the Fisher corpus~\cite{cieri2004fisher} have produced impressive results~\cite{hannun2014deepspeech, hays2008im2gps, krizhevsky2012imagenet} that surpass those obtained from decades of research on analytic methods~\cite{kehoe2015survey}.
This suggests that large-scale machine learning of grasps for vast numbers of possible object shapes, object poses, environment configurations, etc.~\cite{goldfeder2011data, lenz2015deep, kappler2015leveraging}, could exhibit scaling effects similar to those observed in computer vision and speech recognition.

@@

We develop a Multi-Armed Bandit (MAB) algorithm with correlated rewards to scale robust planning by learning from a large dataset of parallel-jaw grasps and 3D object models.
Our algorithm is based on Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}, an efficient model for predicting a belief distribution on the quality of each grasp from prior data.

To study scaling effects we develop Dex-Net 1.0, a new dataset of approximately 10,000 3D object models scaled to fit within a PR2 gripper and selected to reflect objects that could be encountered in warehousing or the home such as tooks tableware, boxes, and toys.
~\figref{dexnet-teaser} shows a sample of the objects in the dataset.
Dex-Net contains laser-scanned 3D mesh models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking} to reflect physical objects commonly used for benchmarking in grasping research.
The dataset also includes synthetic 3D mesh models from shape classification datasets such as 3DNet~\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20143d}, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison} to approach larger scales.
Dex-Net contains approximately 2.5 million parallel-jaw grasps, and each object is labelled with up to 250 grasps and an estimate of the probability of force closure for each under uncertainty in object pose, gripper pose, and friction coefficient.
We also incorporate multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi} to learn a similarity metric between objects based on CNN features  from millions of labeled images, which allows us to efficiently retrieve similar 3D objects from Dex-Net for grasp planning at scale. 
To the best of our knowledge, Dex-Net is the largest dataset to-date used for grasping research.

We implement our algorithm on Google Compute Engine and store Dex-Net on Google Cloud Storage.
Experiments on using our algorithm to plan parallel-jaw grasps with high probability of force closure from 250 candidates suggest that orders of magnitude of prior data can reduce the average number of samples needed for X by Y and \TODO{Robustness statement} on a test set of 30 objects.
Experiments on the sensitivity to the fsimilarity metric and number of nearest neighbors used from Dex-Net suggest...\TODO{Add}
\TODO{Something about the number of instances...}
